\section{Work Experience}
  \resumeSubHeadingListStart
      % Amazon context: Junior SDE experience across two Amazon teams, highlighting independent ownership, security/compliance work, and a greenfield full-stack service that improved spend attribution at scale.
      \resumeSubheading
      {Amazon (RDS \& Billing)}{December 2024 -- Present}
      {Software Development Engineer $|$ Toronto, ON}{}
      \resumeItemListStart
      \resumeItem{In my first month, helped resolve a production issue in an early launch by fixing a sizing bug that could have caused memory overflow and customer data loss.}

      \resumeItem{Built a self-service RDS diagnostics export workflow that let customers send logs to S3 for support, reducing manual support work and improving security.}

      \resumeItem{Owned the feature from design through launch, including security review, threat modeling, and remediation to meet internal standards.}

      \resumeItem{Designed and launched a full-stack cost-tagging platform to help internal teams attribute AWS spend to business goals using React/TypeScript and a Java-based backend on AWS.}

      \resumeItem{Implemented the service with API Gateway, Lambda, S3, DynamoDB, and authorization workflows for tagging, allocation, and reporting.}
      \resumeItemListEnd

     % Naryant - Python and Selenium
    \resumeSubheading
    {Centre for Applied AI \& Naryant}{January 2024 -- April 2024}
    {Software Engineer \& Data Analyst Intern $|$ Oakville, ON}{}
    \resumeItemListStart
    \resumeItem{Modeled traffic patterns with SUMO and OpenStreetMap to improve urban planning simulations across 10+ zones.}
    
    \resumeItem{Built a Python Selenium scraper and ETL pipeline to automate demographic data extraction and transform it into SUMO XML for large-scale simulations.}
    \resumeItemListEnd
      

    \resumeSubheading
  {FreshBooks}{May 2023 -- August 2023}
  {Full-Stack Software Engineer Intern $|$ Toronto, ON}{}
  \resumeItemListStart
  \resumeItem{Led the CI/CD migration from Jenkins to Azure DevOps for 5+ microservices using Docker and Kubernetes, accelerating delivery ahead of schedule.}

  \resumeItem{Improved FreshCLI build efficiency by 34\% and increased developer productivity by introducing reusable Azure pipeline templates and a custom Code Climate task.}
  \resumeItemListEnd

    % TD - Android
    \resumeSubheading
  {TD Bank}{January 2023 -- April 2023}
  {Android Developer Intern $|$ Toronto, ON}{}
  \resumeItemListStart
  \resumeItem{Developed and maintained the TD Bank mobile app in Java and Kotlin, building responsive UI experiences with Jetpack Compose.}

  \resumeItem{Improved REST API loading performance through asynchronous retrieval and caching, reducing JSON load times by 15\% for smoother app interactions.}
  \resumeItemListEnd

      % GEOTAB - Full Stack
    \resumeSubheading
      {GEOTAB}{September 2022 -- December 2022}
      {Software Engineer \& Data Analyst Intern $|$ Oakville, ON}{}
      \resumeItemListStart
      \resumeItem{Developed a city-maintenance web application with React and geospatial analytics for the City of Kingston.}

      \resumeItem{Executed BigQuery geospatial queries and contributed backend refactors to improve scalability and API responsiveness for large datasets.}
      \resumeItemListEnd

      % SIRT Centre - Backend
    % \resumeSubheading
    %   {SIRT Centre}{May 2022 -- August 2022}
    %   {Software Engineer Intern $|$ Toronto, ON}{}
    %   \resumeItemListStart
    %   \resumeItem{Developed AR applications for iOS using Unity and C\#, enabling immersive engagement with 3D avatars}
    
    %   \resumeItem{Researched AR libraries, documenting benchmarks that improved loading times by 3s for better user interaction}

        
      % \resumeItemListEnd

      % \resumeSubheading
      % {Centre for Applied AI, Osteoperosis Canada \& Naryant}{November 2021 -- April 2022}
      % {Machine Learning Engineer \& Data Analyst Intern $|$ Oakville, ON}{}
      % \resumeItemListStart
      % \resumeItem{Led machine learning research to predict Osteoporosis risk using Python \& Scikit-learn, improving predictive accuracy through feature engineering}
      % \resumeItem{Ensured algorithm effectiveness by cleaning thousands of records \& implementing data validation strategies}
  
  
      % % \resumeItem{Conducted machine learning \& data science research to predict the risk of Osteoporosis using Python \& Scikit-learn}
      % % \resumeItem{Performed data cleaning for thousands of patient data records to ensure effective machine learning algorithm performance}
      % % \resumeItem{Developed data validation strategies to ensure high levels of data quality throughout the project lifecycle}
      % % \resumeItem{Implemented feature engineering techniques to enhance the predictive power of datasets}
        
      % \resumeItemListEnd

    \resumeSubHeadingListEnd